\newpage
\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}
\begin{singlespace}
	\emph{Habemus Thesim!\\
		Eminentissimum ac reverendissimum Documentum, et cetra...\\
		(Scribmus latinum sine intellectum)}
\end{singlespace}

First and foremost, I'd like to thank the nameless stranger that is responsible for enforcing the deadline for the submission of this thesis; but for their unwavering absolutism this thesis would exist in a perpetual state of being nearly done.

The rest follows in no particular order.

I'd like to express my deep gratitude to my supervisor, Prof. Luke McCaffrey, who graciously offered his unwaivering support, undivided attention, and inspired insight to myself and all others in our lab. Thank you for this opportunity, on which I'll always think warmly of and be better for.

Fellow students and fellows of McCaffrey lab have, without hesitation or question, taken the time to answer dumb questions, show me their magic ways, and commiserate over the seemingly innumerable and sometimes unimaginable ways an experiment could go wrong. They're also all people I'm very proud to call my dear friends. Thank you Andrew, Daya, Carlis, Christina, Li-Ting, Maia, Ruba, Sara, Sudipa, Virginie and our newest additions Aislynn and Rebecca.

Some of my oldest friends and most esteemed peers, thanks to the DRMTM for their invaluable support: AD, AL, AV, GK, \& PH. \#4MOREYEARS.

My family has always supported me in all things, so I'd like to thank my parents, grandparents, and brother for never failing to do all they can and more to see me succeed. 

I'd like to acknowledge Arthur Samuel and Marvin Minsky, whose seminal works in machine learning, and their contributions to \TeX\xspace and the invention of the confocal microscope, respectively, make them cognitive fathers of this thesis. This thesis was only made possible thanks to the open-source communities that built and maintain the software for everything from the typesetting of this document to the machine learning libraries that power the models in this thesis.
\newpage
Finally, this thesis is dedicated to the memory of the two laptops that gave up their magic smoke in the name of science and this thesis.\\
To my Dell Studio 1555 and Asus Zenbook UXA1:
\begin{singlespace}
	\noindent
	\emph{Do not go gentle into that goodnight\\
		Rage, rage against the dying of the backlight}
\end{singlespace}

